\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-01 gwnnDraft02.tex
minor changes.
fig caption fixes.

\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}

@@

\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa (blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }

>>>>

\caption{ Gravitational wave power spectrum for standard $N$naturalness using the scalar reheaton model of section~\ref{sec:reheat}. All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays as described in Section~\ref{sec:detection}; Lisa (blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green).}

@@

\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom left (right) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves~\cite{PhysRevD.88.124032} calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa (blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
